Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-08-09 volunteer-clouds-ieee-ci-si.tex
Added description of Weibull fit
Which is quite good, BTW.

\begin{figure}[!htb]
\centering
\includegraphics[width=0.9\linewidth]{img/ips-time-ww.png}
\caption{Time employed in every experiment vs. number of IPs (in abscises). The red dot and line show the average and standard deviation, the shade of blue the number of experiments with the same number of IPs. }
\label{fig:ipstime:w2}
\end{figure}
%
%
\begin{table*}
\caption{Summary of fit to Generalized Extreme Value distribution of
  the number of {\tt PUT}s per worker. \label{tab:puts:ww}}
\begin{center}
\begin{tabular}{ccc}
\hline
Location $\mu$ & Scale $\sigma$ & Shape $\xi$ \\
\hline
18.275 $\pm$ 0.83719  &  25.962  $\pm$ 1.22015 & 1.242   $\pm$ 0.04746 \\
\hline
\end{tabular}
\end{center}
\end{table*}
%
\begin{figure}[!htb]
\centering
\includegraphics[width=0.49\linewidth]{img/gev-fit-ww.png}
\includegraphics[width=0.49\linewidth]{img/weibull-fit-ww.png}
\caption{Ranked number of {\tt PUT}s per worker and GEV fit (in red, right) and Weibull (in red, left) for the {\sf NodIO$^2$} model. }  
\label{fig:gev:w2}
\end{figure}
%
It is also interesting to measure the scaling properties in this
model, that is, the relationship between the number of IPs
participating in an experiment and the time it takes to complete
it. This is shown in Figure \ref{fig:ipstime:w2}, which shows every
experiment in a time (in milliseconds) vs. number of workers participating
in it. Although there is not a clear trend, the graph seems to say
that the time needed for finding the solution in this evolutionary
algorithm does not depend on the number of workers participating in
it. This does not mean that it is independent on the number of {\em
  simultaneous} users, which is probably the case although it is more
difficult to measure. There seems to be a trend towards a decreasing
standard deviation in the time, with more volunteers adding {\em
  robustness} to an experiment and certainty in the time it is taking;
however, more experiments would be needed to check this hypothesis.

As we did in the previous subsection, we have fitted also the number
of HTTP {\tt PUT}s per worker to a  Generalized Extreme Value (GEV) function, with the result shown %FERGU: he cambiado GEV por GET (lo de GEV era un error, no? vayamos a que sea algo nuevo que no conozco...)
%cojollos, Fergu, si no conoces no lo cambies. 
in Table \ref{tab:puts:ww}. Comparing this table with what we obtained
in the previous experiment, Table \ref{tab:puts:os}, we find higher values
for the location $\mu$ and scale $\sigma$ parameters, accounting for
the higher number of contributions per volunteer that has been
previously observed; however, the shape $\xi$ parameter is
substantially similar, with a {\em bell} shape leaning towards the
origin, indicating a pattern of a few users with many contributions
and many with few contributions. If we plot the model and the data
side by side, as shown in Figure \ref{fig:gev:w2} we see that the fit
is not so tight as in the previous case, with the model overestimating
the number of individuals with a high number contributions. This is
probably due to the fact that in the previous case, the user needed to
voluntarily reload the page to contribute the most generations, with a
{\em phase change} between the people that did so and the people that
just run the experiment until completion. In this case, however, the
user just needs to let it run, without that phase change and thus a
more {\em equalitarian} distribution of contributions.

>>>>

\begin{figure}[!htb]
\centering
\includegraphics[width=0.9\linewidth]{img/ips-time-ww.png}
\caption{Time employed in every experiment vs. number of IPs (in abscises). The red dot and line show the average and standard deviation, the shade of blue the number of experiments with the same number of IPs. }
\label{fig:ipstime:w2}
\end{figure}
%
%
\begin{table*}
\caption{Summary of fit to Generalized Extreme Value (GEV) and Weibull distribution of
  the number of {\tt PUT}s per worker. \label{tab:puts:ww}}
\begin{center}
\begin{tabular}{cccc}
\hline
Distribution & Location $\mu$ & Scale $\sigma$ & Shape $\xi$ \\
\hline
GEV & 18.275 $\pm$ 0.83719  &  25.962  $\pm$ 1.22015 & 1.242   $\pm$
0.04746 \\
Weibull & ND & 75.11457519 $\pm$ 2.97470251  & 0.69714410 $\pm$ 0.01383976 \\
\hline
\end{tabular}
\end{center}
\end{table*}
%
\begin{figure}[!htb]
\centering
\includegraphics[width=0.49\linewidth]{img/gev-fit-ww.png}
\includegraphics[width=0.49\linewidth]{img/weibull-fit-ww.png}
\caption{Ranked number of {\tt PUT}s per worker and GEV fit (in red, right) and Weibull (in red, left) for the {\sf NodIO$^2$} model. }  
\label{fig:gev:w2}
\end{figure}
%
It is also interesting to measure the scaling properties in this
model, that is, the relationship between the number of IPs
participating in an experiment and the time it takes to complete
it. This is shown in Figure \ref{fig:ipstime:w2}, which shows every
experiment in a time (in milliseconds) vs. number of workers participating
in it. Although there is not a clear trend, the graph seems to say
that the time needed for finding the solution in this evolutionary
algorithm does not depend on the number of workers participating in
it. This does not mean that it is independent on the number of {\em
  simultaneous} users, which is probably the case although it is more
difficult to measure. There seems to be a trend towards a decreasing
standard deviation in the time, with more volunteers adding {\em
  robustness} to an experiment and certainty in the time it is taking;
however, more experiments would be needed to check this hypothesis.

As we did in the previous subsection, we have fitted also the number
of HTTP {\tt PUT}s per worker to a  Generalized Extreme Value (GEV) function, with the result shown %FERGU: he cambiado GEV por GET (lo de GEV era un error, no? vayamos a que sea algo nuevo que no conozco...)
%cojollos, Fergu, si no conoces no lo cambies. 
in Table \ref{tab:puts:ww}. Comparing this table with what we obtained
in the previous experiment, Table \ref{tab:puts:os}, we find higher values
for the location $\mu$ and scale $\sigma$ parameters, accounting for
the higher number of contributions per volunteer that has been
previously observed; however, the shape $\xi$ parameter is
substantially similar, with a {\em bell} shape leaning towards the
origin, indicating a pattern of a few users with many contributions
and many with few contributions. If we plot the model and the data
side by side, as shown in Figure \ref{fig:gev:w2} we see that the fit
is not so tight as in the previous case, with the model overestimating
the number of individuals with a high number contributions. This is
probably due to the fact that in the previous case, the user needed to
voluntarily reload the page to contribute the most generations, with a
{\em phase change} between the people that did so and the people that
just run the experiment until completion. In this case, however, the
user just needs to let it run, without that phase change and thus a
more {\em equalitarian} distribution of contributions, which rather
corresponds to a Weibull function, as shown in Figure
\ref{fig:ipstime:w2} (right hand side). The fitted parameters for this
distribution, shown in Table \ref{tab:puts:ww}, show a shape parameter
equal to 0.69, a value that is remarkably similar to the 0.5 value
found for time devoted to games in Chambers et
al. \cite{chambers2005measurement}.
